### 2017-06-13 manuscript/manuscript.Rmd
Distinguish replicability and reproducibility.

>>>>

Although they are often conlated [TODO] reproducibility and replicability are, in fact, independent of one another. One might think that reproducibility [TODO Peng 2011?] is a requirement of replicability, but an experiment can be replicated even if the materials of the original study are not available for replicability. Likewise, the materials of a study might allow its results to be reproduced, yet the underlying scientific idea might not be replicable. Therefore, it is important to keep these two concepts distinct; in this manuscript we are interested in reproducibility.
